SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-05-15 scipy-1.0/paper.tex

\subsection*{Community beyond the SciPy library}

The scientific Python ecosystem includes many examples
of domain-specific software libraries building on top
of SciPy features, and then returning to the base SciPy library
to suggest and even implement improvements to enable
more effective science applications. For example, there
are common contributors to the SciPy and Astropy core
libraries\cite{astropy-2018}, and what works well for 
one of the codebases, infrastructures, or communities 
is often transferred in some form to the other. At the codebase 
level, the \texttt{binned\_statistic} functionality
is one such cross-project contribution---it was initially
developed in an Astropy-affiliated package
and then placed in SciPy afterwards.

>>>>

\subsection*{Downstream projects}

The scientific Python ecosystem includes many examples
of domain-specific software libraries building on top
of SciPy features and then returning to the base SciPy library
to suggest and even implement improvements. 
For example, there are common contributors to the SciPy and 
Astropy core libraries\cite{astropy-2018}, and what works 
well for one of the codebases, infrastructures, or communities
is often transferred in some form to the other. At the codebase
level, the \texttt{binned\_statistic} functionality
is one such cross-project contribution: it was initially
developed in an Astropy-affiliated package
and then placed in SciPy afterwards. 
In this perspective, SciPy serves as a catalyst for cross-fertilisation 
throughout the Python scientific computing community.
